\bf A Hierarchical Model for Heterogenous Reliability Field Data

### 2018-04-06 paper/m-lb-m-technometrics.tex

\paragraph{Model 2} $t_{p_{2}g}$ varies by drive-model. To help with model identifiably, we tighten the priors on the early failure mode:
$$ \pi \sim \op{Logit-normal}\langle 7.0\times 10^{-3},\, 2.6 \times 10^{-1} \rangle,$$
$$\sigma_1 \sim \op{Lognormal}\langle 1.4 \times 10^{-1},\, 7.1\rangle,$$ 
$$t_{p_1} \sim \op{Lognormal} \langle 2.2 \times 10^1,\, 5.5 \times 10^{4} \rangle.$$

@@

\begin{align*}
  \eta_{\pi} & \sim \op{Normal}(-3, 1)\\
  \tau_{\pi} & \sim \op{Half-Cauchy}(0, 1)\\
  \eta_{\sigma ,2} & \sim \op{Normal}(0, 2)\\
  \tau_{\sigma ,2} & \sim \op{Half-Cauchy}(0, 1)\\
  \eta_{t_{.2_2},2} & \sim \op{Normal}(9, 2)\\
  \tau_{t_{.2_2},2} & \sim \op{Half-Cauchy}(0, 1).
 \end{align*}

>>>>

\paragraph{Model 2} $t_{p_{2}g}$ varies by drive-model. To help with model identifiably, we tighten the priors on the early failure mode:
$$ \pi \sim \op{Logit-normal}\langle 7.0\times 10^{-3},\, 2.6 \times 10^{-1} \rangle,$$
$$\sigma_1 \sim \op{Lognormal}\langle 1.4 \times 10^{-1},\, 7.1\rangle,$$ 
$$t_{0.5} \sim \op{Lognormal} \langle 2.2 \times 10^1,\, 5.5 \times 10^{4} \rangle.$$

@@

\begin{align*}
  \eta_{\pi} & \sim \op{Normal}(-3, 1)\\
  \tau_{\pi} & \sim \op{Half-Cauchy}(0, 1)\\
  \eta_{\sigma_2} & \sim \op{Normal}(0, 2)\\
  \tau_{\sigma_2} & \sim \op{Half-Cauchy}(0, 1)\\
  \eta_{t_{0.2}} & \sim \op{Normal}(9, 2)\\
  \tau_{t_{0.2}} & \sim \op{Half-Cauchy}(0, 1).
 \end{align*}
